### 2019-11-27 paper_lap/05apparatus.tex

\begin{remark1}
We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than a panel length away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ ie. the function $K(\by,\gamma(t)) \in S_\epsilon.$ Thus accurate values of the solution in the far-field can be obtained almost immediately.
\end{remark1}
\begin{remark1}
Similarly, if the point $\by \in \mathbb{R}^2 \setminus \Omega$ at which the solution to the Neumann boundary value problem is to be calculated lies close to a smooth panel then the density $\sigma$ near that point can be interpolated to a finer set of quadrature points and the value of $u(\by)$ can once again be obtained to precision $\epsilon.$ We note, however, that in general the density in the vicinity of a corner cannot be interpolated accurately. This follows from the fact that the interpolation scheme constructed is only guaranteed to interpolate the powers arising in the Dirichlet problem accurately near the corner. The collection of singular powers arising in Neumann problems contain negative powers which are not contained in this set and hence are not interpolated accurately.
\end{remark1}

@@

For a panel $\gamma([s_1,s_2])$ with discretization nodes $x_i,\dots,x_{i+M}$ corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$). Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ (see \cite{} for a detailed description of this process and quantitative estimates on the accuracy of the result). Typically we use 16th order Gauss-Legendre panels and choose their sizes so that their length is no more than their distance to the nearest corner.

@@

We begin with the following proposition, the proof of which follows immediately from the definition of the kernel $k$ and is omitted.
\begin{proposition}
Suppose that $f$ be a piecewise-analytic function in $S_\epsilon$ and  $\underline{\sigma} = (A^T)^{-1} {\bf f}$ is the approximation to the Neumann density obtained using the adjoint of the discretization for the interior Dirichlet boundary integral equation. Then
\begin{align}
h(t) = \sum_{i=P+1}^N k(t,s_i) \sqrt{w_i} \,\underline{\sigma}_i
\end{align}
is an analytic function of $t$ for all $t \in (-\delta,\delta),$ assuming that $s_1,\dots,s_P$ correspond to the discretization of $(-\delta,\delta)$ with the corner point corresponding to $t=0.$
\end{proposition}

In light of this we consider the following integral equation
\begin{align}\label{eqn:resolve_neum0}
-\sigma(s) + \int_{-\delta}^\delta k(s,t) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -\delta \le s \le \delta.
\end{align}
We note that the solution to (\ref{eqn:resolve_neum0}) is equal to the solution of the original boundary integral equation (\ref{bie_extn}) restricted to the interval $[-\delta,\delta].$ Taking the adjoint of (\ref{eqn:resolve_neum0}) we obtain
\begin{align}\label{eqn:resolve_diri0}
-\sigma(s) + \int_{-\delta}^\delta k(t,s) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -\delta \le s \le \delta.
\end{align}
which is a Dirichlet boundary integral equation for a wedge with a piecewise analytic right-hand side. In particular, we can discretize the operator using the method summarized in the previous section. Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{sec:disc_dir} (see \cite{} for a detailed description of the method). Let $\underline{f}_0$ denote the right-hand side of (\ref{eqn:resolve_neum0}) evaluated at these discretization nodes and scaled by the square roots of the corresponding weights. Let $A_0$ be the discretization of the interior Dirichlet problem operator (ie. the operator acting on $\sigma$ on the left-hand side of (\ref{eqn:resolve_diri0})). We note that due to the scale invariance of Laplace's equation for polygonal domains the portion of $A_0$ corresponding to the self-interaction of $L_0$ is a submatrix of the original matrix $A.$ All other blocks can be generated using the discretization nodes as quadrature nodes.

The analysis of the previous section then shows that if $\underline{\sigma}_0$ is the solution of the equation
\begin{align}
A_0^T \underline{\sigma}_0 = \underline{f}_0
\end{align}
then $\underline{\sigma}_0$ gives a {weak solution} to the integral equation (\ref{eqn:resolve_neum0}), i.e. for any function $g$ which is analytic on $[-\delta,0]$ and $[0,\delta]$ the inner product $\langle g,\sigma \rangle$ can be calculated to precision $\epsilon$ using the solution $\underline{\sigma}_0.$ Moreover, since the true density $\sigma$ is smooth on $I_0$ and $J_0$ the Gauss-Legendre discretization allows accurate interpolation of the density on those regions.

@@

The following theorem shows that the right-hand side $\underline{f}_0$ can be computed only using local data (i.e. values of the weak solution in the vicinity of the corner).\\
{\color{red} Manas: there is something a little bad with this proof - Taylor series vs $\epsilon$}
\begin{theorem}
Suppose that $\underline{f}_0$ is the discretization of the right-hand side of (\ref{eqn:resolve_diri0}) corresponding to nodes $s^0_1,\dots,s^0_{N_0}.$ Further suppose that $U$ is the $P\times P$ matrix with entries $U_{ij} = \phi_i(s_j) \sqrt{w_j},$ where $\phi_1,\dots,\phi_P$ are the orthonormal functions on $(-\delta,\delta)$ spanning $,{\rm sgn}(s)|s|^\mu, |s|^\mu,$ $\mu=0,1/2-40$ on that interval. Let $w:(-\delta,\delta) \to \mathbb{R}^P$ be the vector-valued function defined by
\begin{align}
w(t) = (\phi_1(t),\phi_2(t),\dots,\phi_P(t)),
\end{align}
and $\tilde{\sigma} = (\sigma_1,\dots,\sigma_P)^T$ be the approximation to the solution in the vicinity of the corner obtained by solving the original system (\ref{eqn:adj_linalg}). Then $|(f(t)-h(t)) - w(t) U^{-1} A_0^T \tilde{\sigma}| = O(\epsilon)$ for all $t \in(-\delta,\delta).$ In particular, if $\tilde{f}_0$ is the vector of length $N_0$ with entries defined by
\begin{align}
(\tilde{f}_0)_i = w(s^0_i) U^{-1} A_0^T \tilde{\sigma}, \quad i=1,\dots,N_0,
\end{align}
then $\| \underline{f}_0 - \tilde{f}_0\| = O(\epsilon).$
\end{theorem}
\begin{proof}
We begin by observing that both $f$ and $h$ are analytic on the interval $(-\delta,\delta).$ In particular, they can be accurately interpolated using $\phi_1,\dots,\phi_P$ on the interval $(-\delta,\delta).$ In particular, 
\begin{align}\label{eqn:approx_thm}
f(t)-h(t) \approx w(t) U^{-1} (f(s_1)-h(s_1),\dots,f(s_P)-h(s_P))^T
\end{align}
On the other hand, by construction,
\begin{align}\label{eqn:linalg_thm}
\underline{f} = A^T \begin{pmatrix}\tilde{\sigma}\\ \sigma_{P+1}\\ \vdots\\ \sigma_N\end{pmatrix}.
\end{align}
Let $A_0$ be the $P\times P$ submatrix of $A$ corresponding to the first $P$ rows and columns of $A,$ and $A_{\rm red}$ be the $P \times (N-P)$  submatrix of $A$ corresponding to selecting the first $P$ rows of $A$ and all but the first $P$ columns of $A.$ Using this notation, the first $P$ rows of (\ref{eqn:linalg_thm}) can be re-written as
\begin{align}
\begin{pmatrix}f_1\\\vdots \\ f_P\end{pmatrix}  = A_{\rm red}^T \begin{pmatrix} \sigma_{P+1}\\ \vdots\\ \sigma_N\end{pmatrix} + A_0^T \tilde{\sigma}.
\end{align}
The first term on the right-hand side is $(h(s_1),\dots,h(s_P))^T.$ Substituting this into the previous equation, we obtain
\begin{align}
(f(s_1)-h(s_1),\dots,f(s_P)-h(s_P))^T = A_0^T \tilde{\sigma}.
\end{align}
The result follows by substituting the above equality into (\ref{eqn:approx_thm}).
\end{proof}

This can be iterated to obtain an interpolable approximation to the density on $L_0 = [-\delta/2,\delta/2].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $L_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain. In particular, if we define
\begin{align}
h_1(s) = \sum_{x_i \in I_0,J_0} k(s,x_i) \sigma_0^{(i)} \sqrt{w_i}
\end{align}
then $\sigma$ restricted to the interval $L_0$ satisfies
\begin{align}\label{eqn:resolve_neum1}
-\sigma(s) + \int_{-\delta/2}^{\delta/2} k(s,t) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta/2 \le s \le \delta/2.
\end{align}
The corresponding adjoint equation is given by 
\begin{align}\label{eqn:resolve_diri1}
-\sigma(s) + \int_{-\delta/2}^{\delta/2} k(t,s) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta/2 \le s \le \delta/2.
\end{align}

Once again, we divide $L_0$ into three intervals $I_1,$ $L_1,$ and $J_1$ and discretize each interval as before. After solving the corresponding discretization of (\ref{eqn:resolve_neum1}) using the adjoint of the discretization of the integral operator appearing in (\ref{eqn:resolve_diri1}) we obtain a weak solution of $\sigma$ on the interval $L_0$ which can be interpolated on $I_1,$ and $J_1$ to within precision $\epsilon.$

>>>>

\begin{remark1}
We observe that if the solution to the boundary value problem is being calculated at a point $\by \in \mathbb{R}^2\setminus \Omega$ more than {\color{red}two panel lengths} away from the boundary curve $\Gamma$ then the Neumann density $\sigma$ obtained using the above result will give an accuracy of $\epsilon,$ ie. the function $K(\by,\gamma(t)) \in S_\epsilon.$ Thus accurate values of the solution in the far-field can be obtained almost immediately.
\end{remark1}
\begin{remark1}
Similarly, if the point $\by \in \mathbb{R}^2 \setminus \Omega$ at which the solution to the Neumann boundary value problem is to be calculated lies close to a smooth panel then the density $\sigma$ near that point can be interpolated to a finer set of quadrature points and the value of $u(\by)$ can once again be obtained to precision $\epsilon.$ We note, however, that in general the density in the vicinity of a corner cannot be interpolated accurately. This follows from the fact that the interpolation scheme constructed is only guaranteed to interpolate the powers arising in the Dirichlet problem accurately near the corner. The collection of singular powers arising in Neumann problems contain negative powers which are not contained in this set and hence are not interpolated accurately.
\end{remark1}

@@

For a panel $\gamma([s_1,s_2])$ with discretization nodes $x_i,\dots,x_{i+M}$ corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$). Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2$ (see \cite{} for a detailed description of this process and quantitative estimates on the accuracy of the result). Typically we use 16th order Gauss-Legendre panels and choose their sizes so that their length is no more than their distance to the nearest corner. {\color{red}This latter choice guarantees that for any $\epsilon>0$ there exists an $M$ such that if the Gauss-Legendre panels are discretized using an $M$-point Gauss-Legendre rule then the density on that panel can be interpolated to relative precision $\epsilon$ in an $L^2$-sense.}

@@

We begin with the following proposition, the proof of which follows immediately from the definition of the kernel $k$ and is omitted.
\begin{proposition}
Suppose that $f$ be a piecewise-analytic function in $S_\epsilon$ and  $\underline{\sigma} = (A^T)^{-1} {\bf f}$ is the approximation to the Neumann density obtained using the adjoint of the discretization for the interior Dirichlet boundary integral equation. Further suppose that the discretization nodes are ordered so that $s_1,\dots,s_P$ correspond to the corner panel associated with the interval $(-\delta,\delta),$ $s_{P+1},\dots,s_{P+M}$ correspond to the Gauss-Legendre panel immediately to the left associated with the interval $(-2\delta,-\delta),$ and $s_{P+M+1},\dots,s_{P+2M}$ to the Gauss-Legendre panel immediately to the right associated with the interval $(\delta,2\delta).$
Then
\begin{align}
h(t) = \sum_{i=P+2M+1}^N k(s_i,t) \sqrt{w_i} \,\underline{\sigma}_i
\end{align}
is an analytic function of $t$ for all $t \in (-2\delta,2\delta).$
\end{proposition}

In light of this we consider the following integral equation
\begin{align}\label{eqn:resolve_neum0}
-\sigma(s) + \int_{-2\delta}^{2\delta} k(s,t) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta.
\end{align}
We note that the solution to (\ref{eqn:resolve_neum0}) is equal to the solution of the original boundary integral equation (\ref{bie_extn}) restricted to the interval $[-2\delta,2\delta].$ Taking the adjoint of (\ref{eqn:resolve_neum0}) we obtain
\begin{align}\label{eqn:resolve_diri0}
-\sigma(s) + \int_{-2\delta}^{2\delta} k(t,s) \sigma(t)\,{\rm d}t = f(s)-h(s), \quad -2\delta \le s \le 2\delta.
\end{align}
which is a Dirichlet boundary integral equation for a wedge with a piecewise analytic right-hand side. In particular, we can discretize the operator using the method summarized in the previous section. Specifically, we subdivide the interval $[-\delta,\delta]$ into three subintervals $I_0 = [-\delta,\delta/2],$ $L_0 = [-\delta/2,\delta/2],$ and $J_0 = [\delta/2,\delta].$ On $I_0$ and $J_0$ we place standard Gauss-Legendre discretization nodes, while on $L_0$ we use the custom discretization scheme for corners, outlined in Section \ref{sec:disc_dir} (see \cite{} for a detailed description of the method). On the intervals $[-2\delta,-\delta]$ and $[\delta,2\delta]$ we use the same discretization nodes and weights as in the original system for those intervals (we call these panels $K_0$ and $Q_0$ respectively). Let $\underline{f}_0$ denote the right-hand side of (\ref{eqn:resolve_neum0}) evaluated at these discretization nodes and scaled by the square roots of the corresponding weights. Let $A_0$ be the discretization of the interior Dirichlet problem operator (ie. the operator acting on $\sigma$ on the left-hand side of (\ref{eqn:resolve_diri0})). We note that due to the scale invariance of Laplace's equation for polygonal domains the portion of $A_0$ corresponding to the self-interaction of $L_0$ is a submatrix of the original matrix $A.$ All other blocks can be generated using the discretization nodes as quadrature nodes.

The analysis of the previous section then shows that if $\underline{\sigma}_0$ is the solution of the equation
\begin{align}
A_0^T \underline{\sigma}_0 = \underline{f}_0
\end{align}
then $\underline{\sigma}_0$ gives a {weak solution} to the integral equation (\ref{eqn:resolve_neum0}), i.e. for any function $g$ which is analytic on $[-2\delta,0]$ and $[0,2\delta]$ the inner product $\langle g,\sigma \rangle$ can be calculated to precision $\epsilon$ using the solution $\underline{\sigma}_0.$ Moreover, since the true density $\sigma$ is smooth on $[\delta,2\delta]$ and $[-2\delta,-\delta]$ the Gauss-Legendre discretization allows accurate interpolation of the density on those regions.

@@

The following theorem shows that the right-hand side $\underline{f}_0$ can be computed only using local data (i.e. values of the weak solution in the vicinity of the corner).\\
{\color{red} Manas: there is something a little bad with this proof - Taylor series vs $\epsilon$}
\begin{theorem}
Suppose that $\underline{f}_0$ is the discretization of the right-hand side of (\ref{eqn:resolve_diri0}) corresponding to nodes $s^0_1,\dots,s^0_{N_0}.$ Further suppose that $U$ is the $P\times P$ matrix with entries $U_{ij} = \phi_i(s_j) \sqrt{w_j},$ where $\phi_1,\dots,\phi_P$ are the orthonormal functions on $(-\delta,\delta)$ spanning $,{\rm sgn}(s)|s|^\mu, |s|^\mu,$ $\mu=0,1/2-40$ on that interval. Let $w:(-\delta,\delta) \to \mathbb{R}^P$ be the vector-valued function defined by
\begin{align}
w(t) = (\phi_1(t),\phi_2(t),\dots,\phi_P(t)),
\end{align}
and $\tilde{\sigma} = (\sigma_1,\dots,\sigma_P)^T$ be the approximation to the solution in the vicinity of the corner obtained by solving the original system (\ref{eqn:adj_linalg}). Then $|(f(t)-h(t)) - w(t) U^{-1} A_0^T \tilde{\sigma}| = O(\epsilon)$ for all $t \in(-\delta,\delta).$ In particular, if $\tilde{f}_0$ is the vector of length $N_0$ with entries defined by
\begin{align}
(\tilde{f}_0)_i = w(s^0_i) U^{-1} A_0^T \tilde{\sigma}, \quad i=1,\dots,N_0,
\end{align}
then $\| \underline{f}_0 - \tilde{f}_0\| = O(\epsilon).$
\end{theorem}
\begin{proof}
We begin by observing that both $f$ and $h$ are analytic on the interval $(-\delta,\delta).$ In particular, they can be accurately interpolated using $\phi_1,\dots,\phi_P$ on the interval $(-\delta,\delta).$ Hence,
\begin{align}\label{eqn:approx_thm}
f(t)-h(t) \approx w(t) U^{-1} (f(s_1)-h(s_1),\dots,f(s_P)-h(s_P))^T.
\end{align}
{\color{red}A similar argument shows that $f(t)-h(t)$ is interpolable on $[-2\delta,-\delta]$ and $[\delta,2\delta].$}
On the other hand, by construction,
\begin{align}\label{eqn:linalg_thm}
\underline{f} = A^T \begin{pmatrix}\tilde{\sigma}\\ \sigma_{P+{2M+1}}\\ \vdots\\ \sigma_N\end{pmatrix}.
\end{align}
Let $A_0$ be the $(P+2M)\times (P+2M)$ submatrix of $A$ corresponding to the first $P+2M$ rows and columns of $A,$ and $A_{\rm red}$ be the $P+2M \times (N-P-2M)$  submatrix of $A$ corresponding to selecting the first $P+2M$ rows of $A$ and all but the first $P+2M$ columns of $A.$ Using this notation, the first $P+2M$ rows of (\ref{eqn:linalg_thm}) can be re-written as
\begin{align}
\begin{pmatrix}f_1\\\vdots \\ f_{P+2M}\end{pmatrix}  = A_{\rm red}^T \begin{pmatrix} \sigma_{P+2M+1}\\ \vdots\\ \sigma_N\end{pmatrix} + A_0^T \tilde{\sigma}.
\end{align}
The first term on the right-hand side is $(h(s_1),\dots,h(s_{P+2M}))^T.$ Substituting this into the previous equation, we obtain
\begin{align}
(f(s_1)-h(s_1),\dots,f(s_{P+2M})-h(s_{P+2M}))^T = A_0^T \tilde{\sigma}.
\end{align}
The result follows by substituting the above equality into (\ref{eqn:approx_thm}).
\end{proof}

This can be iterated to obtain an interpolable approximation to the density on $L_0 = [-\delta,\delta].$ In particular, we consider the restriction of the exterior Neumann integral equation, as well as its, adjoint to the interval $I_0$ and $J_0.$ For the right-hand side we use the original right-hand side $f$ minus the contribution from the remainder of the domain. In particular, if we define
\begin{align}
h_1(s) = \sum_{x_i \in K_0,Q_0} k(s,x_i) \sigma_0^{(i)} \sqrt{w_i}
\end{align}
then $\sigma$ restricted to the interval $I_0\cup L_0 \cup J_0$ satisfies
\begin{align}\label{eqn:resolve_neum1}
-\sigma(s) + \int_{-\delta}^{\delta} k(s,t) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta \le s \le \delta.
\end{align}
The corresponding adjoint equation is given by 
\begin{align}\label{eqn:resolve_diri1}
-\sigma(s) + \int_{-\delta}^{\delta} k(t,s) \sigma(t)\,{\rm d} t = f(s)-h(s)-h_1(s), \quad -\delta \le s \le \delta.
\end{align}

Once again, we divide $L_0$ into three intervals $I_1,$ $L_1,$ and $J_1$ and discretize each interval as before. After solving the corresponding discretization of (\ref{eqn:resolve_neum1}) using the adjoint of the discretization of the integral operator appearing in (\ref{eqn:resolve_diri1}) we obtain a weak solution of $\sigma$ on the interval $I_0\cup L_0 \cup J_0$ which can be interpolated on $I_0,$ and $J_0$ to within precision $\epsilon.$
